### 2021-04-22 input/proposal.tex
meow

At any time, a \process can decide to become a source, hence creating
a new partition in the system by executing an \texttt{Add}
operation. This partition includes at least its source plus
neighboring \processes that estimate they are closer to this source
than any other source. Such distance (or \emph{weight}) is
application-dependant: in the context of maintaining distributed
indexes, weights would be link latency.

@@

At any time, a source can revoke its self-appointed status of source,
hence deleting its partition from the system, by executing a
\texttt{Del} operation. All \processes that belong to this partition
must eventually choose another partition to belong to. In
Figure~\ref{fig:del}, two partitions exist initially: $P_a$ and $P_d$
that respectively include $\{a\}$, and $\{b, c, d\}$. In
Figure~\ref{fig:delA}, \Process $a$ deletes its partition. It notifies
all neighboring \processes -- here only \Process $b$ -- that may
belong to its partition using \NAMEB. Upon receipt, \Process $b$
discards the message $\delta_a$, for the latter does not target the
former's partition. \Process $b$ sends its own knowledge of best
partition $\alpha_d^3$ that may prove to be the best for \Process
$a$. Eventually, every \processes belong to the same partition
$P_d$. In this scenario, they reach consistent partitioning.

>>>>

At any time, a \process can decide to become a source, hence creating
a new partition in the system by executing an \texttt{Add}
operation. This partition includes at least its source plus
neighboring \processes that estimate they are closer to this source
than any other one. Such distance (or \emph{weight}) is
application-dependant: in the context of maintaining distributed
indexes, weights would be link latency.

@@

At any time, a source can revoke its self-appointed status of source,
by executing a \texttt{Del} operation, hence deleting its partition
from the system. All \processes that belong to this partition must
eventually choose another partition to belong to. In
Figure~\ref{fig:del}, two partitions exist initially: $P_a$ and $P_d$
that respectively include $\{a\}$, and $\{b, c, d\}$. In
Figure~\ref{fig:delA}, \Process $a$ deletes its partition. It notifies
all neighboring \processes -- here only \Process $b$ -- that may
belong to its partition using \NAMEB. Upon receipt, \Process $b$
discards the message $\delta_a$, for the latter does not target the
former's partition. \Process $b$ sends its own knowledge of best
partition $\alpha_d^3$ that may prove to be the best for \Process
$a$. Eventually, every \processes belong to the same partition
$P_d$. In this scenario, they reach consistent partitioning.
